%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,10pt]{extarticle}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue,
]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontspec}   %加這個就可以設定字體
\usepackage{xeCJK}       %讓中英文字體分開設置

\setCJKmainfont{Noto Serif TC}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\definecolor{highlight}{RGB}{0, 91, 114}

% Adjust margins


\addtolength{\textwidth}{1in}


\addtolength{\textheight}{1in}

\usepackage[
top=1cm,
bottom=0.75cm,
left=1cm,
right=1.25cm,
]{geometry} 


\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Huge Katrina (Tsui-Yi) Hung}} \\
  Email: \href{mailto:hong.tsui.yi@gmail.com}{\underline{hong.tsui.yi@gmail.com}} & Github: \href{https://github.com/ZaWarudo87}{\underline{https://github.com/ZaWarudo87}} \\
  Mobile: +886-918-800-719 & Website: \href{https://zawarudo87.github.io/my_portfolio}{\underline{https://zawarudo87.github.io/my\_portfolio}} \\
  Linkedin: \href{www.linkedin.com/in/katrina20050719}{\underline{www.linkedin.com/in/katrina20050719}} & C++, Python, JavaScript, PHP \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Yang Ming Chiao Tung University}{Sep. 2023 - Jun. 2027 (expected)}
      {}{Hsinchu, Taiwan}
      Relevant Course Grades: 
      \vspace{-0.5em}
	\begin{itemize}
	    \item Introduction to Computers and Programming - A+
	    \item Object-Oriented Programming - A+
	    \item Basic Programming - A+
	    \item Competitive Programming(I) - A-
	    \item Linear Algebra - A+
	\end{itemize}
    \resumeSubHeadingListEnd

\vspace{0.1em}
%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
C++ | Python | HTML | CSS | JavaScript | Node.js | PHP | MySQL | Linux | Arduino | Raspberry PI
    \resumeSubHeadingListEnd

\vspace{0.1em}
%-----------LEADERSHIP & ACTIVITIES-----------------
\section{Leadership \& Activities}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NYCU Makereal Labs (Maker Club)}{Feb. 2024 - Present}
      {9th \textcolor{highlight}{Executive} - \textcolor{highlight}{Teaching} and Artistic Design}{}
	\begin{itemize}
	    \item \textcolor{highlight}{Develop projects and teach} production methods and programming in community courses.
	    \item \textcolor{highlight}{Collaborate with teaching staff} to create projects and courses for maker camps and workshops, including competitive elements for participants.
	    \item Design the club mascot, promotional materials, and so on; utilize \textcolor{highlight}{electronics} and modeling knowledge for club souvenirs.
	    \item Represent the club and school in \textcolor{highlight}{makerthons} together.
	\end{itemize}

    \resumeSubheading
      {2024 NYCU Maker’s Summer Camp}{Apr. 2024 - Jul. 2024}
      {\textcolor{highlight}{Director} - \textcolor{highlight}{Courses} and Artistic Design}{}
	\begin{itemize}
	    \item Served as a \textcolor{highlight}{C++ program director} and project ideation instructor; \textcolor{highlight}{prepared syllabus and guide staff}; 86\% of participants were satisfied with this course.
	    \item Be a \textcolor{highlight}{teaching assistant} and group counselor, helping team cohesion, curriculum progress, problem-solving, and makerthon participation.
	\end{itemize}

    \resumeSubheading
      {2024 NYCU × CPSHS JavaScript Workshop}{May 2024 - Jul. 2024}
      {Staff Member - Artistic Design \& Teaching Assistant}{}
	\begin{itemize}
	    \item Designed event posters.
	    \item Assisted students with questions and ensured they kept up with the course progress.
	    \item Provided lesson preparation suggestions to the instructor.
	\end{itemize}

    \resumeSubheading
      {2024 NYCU Management Science Leadership Camp (Mansion of Savior)}{Feb. 2024 - Jul. 2024}
      {Staff Member - Artistic Design \& Internet Publicity Department}{}
	\begin{itemize}
	    \item Designed event avatars and created props needed for camp activities.
	    \item Assisted group counselors in managing team members and prepared performances and game activities with other staff members.
	\end{itemize}

    \resumeSubheading
      {2024 NYCU Maker’s Winter Camp}{Nov. 2023 - Jan. 2024}
      {Staff Member - \textcolor{highlight}{C++ Program Instructor}}{}
	\begin{itemize}
	    \item \textcolor{highlight}{Coordinated} C++ instructors’ syllabus, scope, and duration in class; \textcolor{highlight}{prepared and taught C++ courses}; 95\% of participants were satisfied with this course.
	    \item Acted as a teaching assistant and group counselor, ensuring progress and addressing issues.
	\end{itemize}
    \resumeSubHeadingListEnd

\vspace{0.1em}
%-----------AWARDS & PROJECTS-----------------
\section{Awards \& Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Alcohol Interlock - technical application and performance analysis}{Mar. 2024 - May 2024}
      {2024 MakeNTU AUO Corporate \textcolor{highlight}{Award Third Place}}{}
	\begin{itemize}
	    \item We developed an alcohol interlock that continuously monitors the driver’s alcohol reaction by several indicators during driving.
	    \item It includes a humorous generative AI virtual assistant aiming to address the flaws and inconveniences of current alcohol interlocks.
	    \item Alongside four partners, I co-created and competed in a \textcolor{highlight}{makerthon} project. My responsibilities are handling the simulation of the car interface \textcolor{highlight}{webpage} and integrating the \textcolor{highlight}{ChatGPT API} to make our alcohol interlock provide relevant feedback based on backend data.
	\end{itemize}

\newpage %next page
    \resumeSubheading
      {GPE}{March 20, 2024}
      {Score: 450 / 600; Rank: 4 / 87}{}
	\begin{itemize}
	    \item A GPE score of 240 is the graduation threshold for the Department of Computer Science at NYCU. It’s more challenging than the CPE (Collegiate Programming Examination).
	    \item This is the grading standard for Basic Programming, and I achieved A+.
	\end{itemize}

    \resumeSubheading
      {1A2B - The Web Game}{Mar. 2023}
      {Midterm Project for Information Technology Course}{}
	\begin{itemize}
	    \item Developed a website for playing the classic game 1A2B, featuring registration and login to record best scores and join the leaderboard.
	    \item Built using \textcolor{highlight}{HTML + CSS + JavaScript and PHP}, hosted on WampServer, and stored player data in \textcolor{highlight}{MySQL}.
	    \item During the class's free viewing period, over 58\% of classmates participated in the 1A2B online ranking battle, with over 70\% playing more than three games.
	\end{itemize}

    \resumeSubheading
      {When Dino Hits the Genetic Algorithm}{Jun. 2022}
      {Final Report for Information Technology Course}{}
	\begin{itemize}
	    \item Attempted to crack the Chrome Dino game using the \textcolor{highlight}{Genetic Algorithm}.
	    \item Utilized \textcolor{highlight}{C++} to cultivate strong genes for 10 generations, each with a gene pool of 100 sets, a 10\% crossover mutation rate, and approximately 1.9 × 10²⁶⁶ possible genes. Integrated the cultivated genes into a modified \textcolor{highlight}{JavaScript} from GitHub to auto-control Dino getting scores and leaving the superior genes.
	\end{itemize}

    \resumeSubheading
      {Big Data × Stock Market}{Feb. 2022 - Jun. 2022}
      {Autonomous Learning Final Presentation Project}{}
	\begin{itemize}
	    \item \textcolor{highlight}{Scraped} 20 years of monthly K-line data for FTSE TWSE Taiwan 50 Index components \textcolor{highlight}{using Python}; backtested parameter combinations and created \textcolor{highlight}{analysis charts with Matplotlib} to identify the most profitable strategy.
	    \item Backtesting with optimal parameters and trading one board lot at a time showed a potential profit of nearly NT\$40,000,000 over 20 years.
	\end{itemize}

    \resumeSubheading
      {Coding With Us!}{Mar. 2022}
      {Project for 2022 \textcolor{highlight}{Google Solution Challenge}}{}
	\begin{itemize}
	    \item Developed an Android app with App Inventor for offline \textcolor{highlight}{C++ and Python learning} to support \textcolor{highlight}{SDGs Quality Education}.
	    \item The app features a cute interface and fun mini-games in each chapter to enhance programming learning enjoyment.
	    \item \textcolor{highlight}{Co-edited HTML format tutorials}, created the project with three partners and joined Google Solution Challenge as a GDSC TMU Project X member.
	    \item I was mainly responsible for conveying competition information, \textcolor{highlight}{project coordination, coding, interface and artwork design, app content planning}, and intro video editing.
	\end{itemize}
    \resumeSubHeadingListEnd
\end{document}